---
title: "Trait factors given face features"
author: "Zarrar Shehzad"
date: "February 15, 2017"
output:
  html_document:
    toc: yes
---

## Overview

Something about what's going on here.

## Setup

Load a bunch of packages and functions.

```{r}
# Path for my own packages
if (!any(.libPaths() == "/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2")) .libPaths(c("/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2", .libPaths()))
if (!any(.libPaths() == "/home/zshehzad/R_libs")) .libPaths(c("~/R_libs", .libPaths()))

# General workhorse function
library(plyr)

# Parallelization
suppressMessages(library(doMC))
registerDoMC(24)

# If we were to use ggplot2 and other plotting needs
library(RColorBrewer)
library(ggplot2)
source("/data1/famface01/command/encoding/FirstPass/plot_functions.R")

# This gets us the simple_lm function for faster GLMs
source("/data1/famface01/command/encoding/SubRois_Unfam/lm_functions.R")

## For heatmap.2
#suppressMessages(library(gplots))
## For our own custom convolution
#source("/data1/famface01/command/encoding/ShapesAnalysis/000_funs_load_convolve.R")
```

And some general variable of interest.

```{r}
subjects <- sprintf("sub%02i", 1:6) # again skipping sub01
#indir    <- "/data1/famface01/analysis/encoding/ShapeAnalysis/data"
rnames   <- c("r.vATL","r.aFFA", "r.pFFA", "r.OFA", "r.EBA", 'r.Amyg', 
              "l.vATL", "l.FFA", "l.OFA", "l.EBA", 'l.Amyg')
```


### Load

First, get the ROI data.

```{r}
load.cur <- function(subj) {
  indir <- "/data1/famface01/analysis/encoding/ShapeAnalysis/data"
  infile <- sprintf("%s/roi_n_more_%s.rda", indir, subj)
  dat <- NULL
  load(infile)
  dat
}

dat.vols <- lapply(subjects, load.cur)
names(dat.vols) <- subjects
```

Second, get the AFNI design matrix from our voxelwise analysies.

```{r}
get.xmat.labs <- function(fn) {
  str <- system(sprintf("grep ColumnLabels %s | sed s/'#  ColumnLabels = '//", fn), intern=T)
  str <- gsub("\"", "", str)
  cols <- strsplit(str, ' ; ')[[1]]
  cols
}

xmat_template <- "/data1/famface01/analysis/task_activity/%s/face_basics_unfam/traitsfa_givenshape.reml/xmat.1D"
lst.xmats <- lapply(subjects, function(subj) {
  xmat_file <- sprintf(xmat_template, subj)
  xmat <- read.table(xmat_file)
  
  # Format the columnnames
  colnames(xmat) <- get.xmat.labs(xmat_file)
  colnames(xmat) <- sub("#0$", "", colnames(xmat))
  colnames(xmat) <- sub("Pol$", "", colnames(xmat))
  
  # Remove the run vars since we centered our data
  xmat <- xmat[,-grep("^Run", colnames(xmat))]
  
  xmat
})
xmats <- do.call(rbind, lst.xmats)

# Add a factor for subjects
subvar <- lapply(1:length(lst.xmats), function(i) rep(subjects[i],nrow(lst.xmats[[i]])))
subvar <- unlist(subvar)
xmats  <- cbind(subject=subvar, xmats)
## create a second version where expand the subject variable
subvar2 <- as.matrix(model.matrix(model.frame(~subvar)))
xmats2 <- cbind(subvar2, xmats[,-1])

# Let's take a peak
head(xmats)
```

Finally load the trait factors as a reference.

```{r}
trait.df <- load.traits()
trait.fa <- factanal(trait.df, factors = 6, rotation = "varimax", 
                     na.action = na.omit, scores="regression")

# plot it
library(corrplot)
hc1     <- hclust(dist(trait.fa$loadings))
hc1     <- as.dendrogram(hc1)
ord.hc1 <- order.dendrogram(hc1)
loading <- trait.fa$loadings[ord.hc1,]
col <- rev(colorRampPalette(c("#67001F", "#B2182B", "#D6604D", 
                            "#F4A582", "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE", 
                            "#4393C3", "#2166AC", "#053061"))(200))
corrplot(loading, tl.col='black', tl.cex=.75, diag=T, col=col, is.corr=T)
```

Based on this plot, we can have some labels for each factor

```{r}
fac.labs <- c("Unemotional", "Competent", "Trustworthy", 
              "Memorable", 'Typical', 'Attractive')
fac.labs2 <- sprintf("%s Factor", fac.labs)
```

Oh and one more thing, let's load the raw trait factor scores as regressors. This
has been done before so just loading it in.

```{r}
base1 <- '/data1/famface01/command/misc/face_representations/300_task_activity/150_face_basics_unfam/'
rdafile <- file.path(base1, "42_trait_n_rois_convolve.rda")
load(rdafile) # see `conv.traitsfa`
```


## ROI Time-Series

### Average

We compile the average of each ROI (for now).

```{r}
lst.rdats <- lapply(dat.vols, function(dat) {
  rdats <- sapply(dat$fmri$dat, rowMeans)
  rdats
})
rdats <- do.call(rbind, lst.rdats)
```

### Model Fitting

Run a regression followed by some contrasts.

```{r}
fit <- simple_lm(rdats, xmats2)
tvals <- fit$tvals[-c(1:6,7:8,21:26),,drop=F]
barplot(tvals, beside = T)
```

#### Contrast: Shape/Texture > Resid

We will do something a little funny with the contrasts. I want to compare the 
shape/texture > residual results for the absolute t-value not the based on the
signed data. So to get this to work, I'm flipping my contrasts if the t-value
is negative for either shape/texture or residuals. This has the effect of 
comparing the absolute values of the fit for that regressor.

```{r}
cfit1.tvals <- sapply(1:ncol(rdats), function(i) {
  fit <- simple_lm(rdats[,i], xmats2)
  tvals <- fit$tvals[-c(1:6,7:8,21:26),,drop=F]
  
  # contrasts: shape > resid
  cons1 <- matrix(0, 6, nrow(fit$b))
  diag(cons1[,grep("shape_", colnames(xmats2))]) <- 1 * sign(tvals[1:6])
  diag(cons1[,grep("resid_", colnames(xmats2))]) <- -1 * sign(tvals[-c(1:6)])
  cfit1 <- simple_contrasts(fit, cons1)
  cfit1$tvals
})
colnames(cfit1.tvals) <- rnames

#fit <- simple_lm(rdats, xmats2)
#tvals <- fit$tvals[-c(1:6,7:8,21:26),,drop=F]
## contrasts: shape > resid
#cons1 <- matrix(0, 6, nrow(fit$b))
#diag(cons1[,grep("shape_", colnames(xmats2))]) <- 1 
#diag(cons1[,grep("resid_", colnames(xmats2))]) <- -1
#cfit1 <- simple_contrasts(fit, cons1)

## contrasts: shape + resid
#cons2 <- matrix(0, 6, nrow(fit$b))
#diag(cons2[,grep("shape_", colnames(xmats2))]) <- 0.5
#diag(cons2[,grep("resid_", colnames(xmats2))]) <- 0.5
#cfit2 <- simple_contrasts(fit, cons2)
#cfit2$tvals

# plot
plot.ts(cbind(scale(rdats[,1]), scale(fitted(fit2)))[1:100,], plot.type = "single", col=2:3)
```

#### Contrast: Shape/Texture + Resid

We also want to run a contrast using the combined shape/texture and residual results. So this would be
used for the overall fit.

```{r}
# Get the regressors together
traitsfa <- do.call(rbind, conv.traitsfa)
colnames(traitsfa) <- sprintf("trait%i", 1:6)
xmats3 <- xmats2[,-grep("_trait", colnames(xmats2))] # remove shape/resid
xmats3 <- cbind(xmats3, traitsfa) # add in the only trait factors

# Fit the model
cfit2 <- simple_lm(rdats, xmats3)
cfit2.tvals <- cfit2$tvals[15:20,]
```

## Plotting

### Setup

We have to convert the different results into data frames for plotting later. First, we compile the tvals
for the shpae/residual data.

```{r}
tvals <- fit$tvals[-c(1:6,7:8,21:26),]
df.tvals0 <- reshape2::melt(tvals)

# split up the first column that has shape_trait1 etc
out.type <- sub("_trait[0-9]", "", df.tvals0[,1])
fac.num <- as.numeric(sub("[a-z_]*", "", df.tvals0[,1]))
#fac.name <- fac.labs[fac.num]
fac.name <- sprintf("%i-%s", 1:6, fac.labs)[fac.num]

# get the hemisphere and rename the ROI column
hemis <- substr(df.tvals0[,2], 0, 1)
rois  <- sub("[.]", " ", df.tvals0[,2])

# remake the df
df.tvals <- data.frame(Regressor=out.type, Factor=fac.name, Hemi=hemis, ROI=rois, Tstat=df.tvals0[,3])
df.tvals$Regressor <- factor(df.tvals$Regressor, levels=c("shape", "resid"))
df.tvals$ROI <- factor(df.tvals$ROI, levels=sub("[.]", " ", rnames))

head(df.tvals)
```

Now we get the data-frames for the contrasts.

```{r}
## CONTRASTS 1
df.tvals0 <- reshape2::melt(cfit1$tvals)
# First column is the contrast of a factor, rename
fac.name <- sprintf("%i-%s", 1:6, fac.labs)[df.tvals0[,1]]
# Second column are the hemis and ROI renames
hemis <- substr(df.tvals0[,2], 0, 1)
rois  <- sub("[.]", " ", df.tvals0[,2])
# Put it together
df.tvals1 <- data.frame(Factor=fac.name, Hemi=hemis, ROI=rois, Tstat=df.tvals0[,3])
df.tvals1$ROI <- factor(df.tvals1$ROI, levels=sub("[.]", " ", rnames)) # make the order right!

## CONTRASTS 2
df.tvals0 <- reshape2::melt(cfit2.tvals)
# First column is the contrast of a factor, rename
fac.name <- sprintf("%i-%s", 1:6, fac.labs)[as.numeric(sub("trait", "", df.tvals0[,1]))]
# Second column are the hemis and ROI renames
hemis <- substr(df.tvals0[,2], 0, 1)
rois  <- sub("[.]", " ", df.tvals0[,2])
# Put it together
df.tvals2 <- data.frame(Factor=fac.name, Hemi=hemis, ROI=rois, Tstat=df.tvals0[,3])
df.tvals2$ROI <- factor(df.tvals2$ROI, levels=sub("[.]", " ", rnames)) # make the order right!
```

### Overall Effect

Let's start by looking at the overall effect. The first plot below is for the 
right hemisphere followed by ones for the left-hemisphere. Note that the scale
is kept to be the same on the left and right hemisphere.

```{r}
ggplot(subset(df.tvals2, Hemi=='r'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("T-statistic") + ylim(min(df.tvals2$Tstat), max(df.tvals2$Tstat)) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals2, Hemi=='l'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("T-statistic") + ylim(min(df.tvals2$Tstat), max(df.tvals2$Tstat)) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Raw T-Vals

#### Effect of Shape/Texture

We only look at the predicted trait factors based on shape/texture information.
Note that the scale here is the same not only for the left/right hemisphere but
also for the residuals plots later.

```{r}
ggplot(subset(df.tvals, Hemi=='r' & Regressor=='shape'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("Shape/Texture T-statistic") + ylim(min(df.tvals$Tstat), max(df.tvals$Tstat)) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals, Hemi=='l' & Regressor=='shape'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("Shape/Texture T-statistic") + ylim(min(df.tvals$Tstat), max(df.tvals$Tstat)) +  
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#### Effect of Residuals

```{r}
ggplot(subset(df.tvals, Hemi=='r' & Regressor=='resid'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("Residual T-statistic") + ylim(min(df.tvals$Tstat), max(df.tvals$Tstat)) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals, Hemi=='l' & Regressor=='resid'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("Residual T-statistic") + ylim(min(df.tvals$Tstat), max(df.tvals$Tstat)) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#### Combine

For seeing both things together.

```{r}
ggplot(subset(df.tvals, Hemi=='r'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor, alpha=Regressor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("T-statistic") + ylim(min(df.tvals$Tstat), max(df.tvals$Tstat)) + 
  bar_theme() + 
  scale_alpha_manual(values=c(1, 0.4)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals, Hemi=='l'), aes(x=Factor, y=Tstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor, alpha=Regressor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("T-statistic") + ylim(min(df.tvals$Tstat), max(df.tvals$Tstat)) + 
  bar_theme() + 
  scale_alpha_manual(values=c(1, 0.4)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```




### Raw T-Vals

#### Effect of Shape/Texture

We only look at the predicted trait factors based on shape/texture information.
Note that the scale here is the same not only for the left/right hemisphere but
also for the residuals plots later.

```{r}
ggplot(subset(df.tvals, Hemi=='r' & Regressor=='shape'), aes(x=Factor, y=abs(Tstat))) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  facet_wrap(~ROI) + 
  ylab("Shape/Texture Abs(T-stat)") + ylim(0, max(abs(df.tvals$Tstat))) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals, Hemi=='l' & Regressor=='shape'), aes(x=Factor, y=abs(Tstat))) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  facet_wrap(~ROI) + 
  ylab("Shape/Texture Abs(T-stat)") + ylim(0, max(abs(df.tvals$Tstat))) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#### Effect of Residuals

```{r}
ggplot(subset(df.tvals, Hemi=='r' & Regressor=='resid'), aes(x=Factor, y=abs(Tstat))) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  facet_wrap(~ROI) + 
  ylab("Residual abs(T-stat)") + ylim(0, max(abs(df.tvals$Tstat))) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals, Hemi=='l' & Regressor=='resid'), aes(x=Factor, y=abs(Tstat))) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  facet_wrap(~ROI) + 
  ylab("Residual abs(T-stat)") + ylim(0, max(abs(df.tvals$Tstat))) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#### Combine

For seeing both things together.

```{r}
ggplot(subset(df.tvals, Hemi=='r'), aes(x=Factor, y=abs(Tstat))) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor, alpha=Regressor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  facet_wrap(~ROI) + 
  ylab("abs(T-stat)") + ylim(0, max(abs(df.tvals$Tstat))) + 
  bar_theme() + 
  scale_alpha_manual(values=c(1, 0.4)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals, Hemi=='l'), aes(x=Factor, y=abs(Tstat))) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor, alpha=Regressor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  facet_wrap(~ROI) + 
  ylab("abs(T-stat)") + ylim(0, max(abs(df.tvals$Tstat))) + 
  bar_theme() + 
  scale_alpha_manual(values=c(1, 0.4)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


#### Feats > Resids

And we can see the contrast between the two. Note if feats > resid is positive
but feats + resid is negative, then we should slip this...so basically we are
looking at abs(feats) > abs(resid).

```{r}
df.tvals1$AbsTstat <- df.tvals1$Tstat * sign(df.tvals2$Tstat)

ggplot(subset(df.tvals1, Hemi=='r'), aes(x=Factor, y=AbsTstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed', color="grey50") + 
  facet_wrap(~ROI) + 
  ylab("Feats > Resid T-statistic") + ylim(min(df.tvals1$AbsTstat), max(df.tvals1$AbsTstat)) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(subset(df.tvals1, Hemi=='l'), aes(x=Factor, y=AbsTstat)) + 
  geom_hline(yintercept = 0) + 
  geom_bar(stat="identity", position=position_dodge(), colour="black", aes(fill=Factor)) + 
  geom_hline(yintercept = 1.96, linetype='dashed') +
  geom_hline(yintercept = -1.96, linetype='dashed') + 
  facet_wrap(~ROI) + 
  ylab("Feats > Resid T-statistic") + ylim(min(df.tvals1$AbsTstat), max(df.tvals1$AbsTstat)) + 
  bar_theme() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



```{r}
## future
# library(lme4)
#rdat <- rdats[,6]
#fit2 <- lmer(rdat ~ faces + quests + shape_trait1 + shape_trait2 + shape_trait3 + shape_trait4 + shape_trait5 + shape_trait6 + resid_trait1 + resid_trait2 + resid_trait3 + resid_trait4 + resid_trait5 + resid_trait6 + roll + pitch + yaw +  dS + dL + dP + (1|subject), data=xmats)
#summary(fit2)
```


