---
title: "ROI Regressions"
author: "Zarrar Shehzad"
date: "February 23, 2017"
output: html_document
    fig_width: 10
    number_sections: yes
    toc: yes
---

## Setup

Load a bunch of packages and functions.

```{r}
# Path for my own packages
if (!any(.libPaths() == "/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2")) .libPaths(c("/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2", .libPaths()))
if (!any(.libPaths() == "/home/zshehzad/R_libs")) .libPaths(c("~/R_libs", .libPaths()))

# General workhorse function
library(plyr)

# Parallelization
suppressMessages(library(doMC))
registerDoMC(24)

# If we were to use ggplot2 and other plotting needs
library(RColorBrewer)
library(ggplot2)
source("/data1/famface01/command/encoding/FirstPass/plot_functions.R")

# This gets us the simple_lm function for faster GLMs
source("/data1/famface01/command/encoding/SubRois_Unfam/lm_functions.R")

## For heatmap.2
#suppressMessages(library(gplots))
## For our own custom convolution
#source("/data1/famface01/command/encoding/ShapesAnalysis/000_funs_load_convolve.R")
```

And some general variable of interest.

```{r}
subjects <- sprintf("sub%02i", 1:6) # again skipping sub01
#indir    <- "/data1/famface01/analysis/encoding/ShapeAnalysis/data"
rnames   <- c("r.vATL","r.aFFA", "r.pFFA", "r.OFA", "r.EBA", 'r.Amyg', 
              "l.vATL", "l.FFA", "l.OFA", "l.EBA", 'l.Amyg')
```


### Load

#### Predicted/Residual Face Features

Actually first load the predicted/residual face features.

```{r}
indir <- "/data1/famface01/analysis/misc/320_roi_task_activity"
load(file.path(indir, "20_predict_face_feats.rda"), verbose=T)
vnames <- demo.vnames
```

#### Convolve Features

Second convolve the different features including faces. We load from what's been done before.

```{r}
ifile <- "/data1/famface01/analysis/misc/320_roi_task_activity/22_convolve_facefeats.rda"
load(ifile, verbose=T)
```

#### ROI Data

Then first, get the ROI data.

```{r}
load.cur <- function(subj) {
  indir <- "/data1/famface01/analysis/encoding/ShapeAnalysis/data"
  infile <- sprintf("%s/roi_n_more_%s.rda", indir, subj)
  dat <- NULL
  load(infile)
  dat
}

dat.vols <- lapply(subjects, load.cur)
names(dat.vols) <- subjects
```

#### Average ROI Time-Series

We compile the average of each ROI (for now).

```{r}
lst.rdats <- lapply(dat.vols, function(dat) {
  rdats <- sapply(dat$fmri$dat, rowMeans)
  rdats
})
rdats <- do.call(rbind, lst.rdats)

load("/data1/famface01/analysis/misc/320_roi_task_activity/std_roi_dat.rda", verbose=T)
```


## Regressions

```{r}
X <- model.matrix(~ssubs + smcs + sfaces + smats)
fit <- simple_lm(std.rdats2, X)
fit$tvals
```

Plot as heatmap

```{r}
cols <- colorRampPalette(rev(brewer.pal(11, "RdBu")))(100)
all.grps2 <- c("face",all.grps)
ccols <- factor(all.grps2, levels=levels(factor(all.grps2)), 
                labels=rev(brewer.pal(length(unique(all.grps2)), "Set3")))
ccols <- as.character(ccols)

mat <- t(fit$tvals[-c(1:12),])
colnames(mat) <- sub("smats", "", colnames(mat))

tmat <- mat * (abs(mat) > 1.96)
#hc.cols <- hclust(dist(t(tmat)), method="ward.D2")
zlim <- max(abs(tmat)) * c(-1,1)
tmat[tmat==0] <- NA

# separator lines
seplines <- c(0,cumsum(rle(all.grps2)$lengths)) + 0.5

heatmap(tmat, scale="none", col=cols, ColSideColors = ccols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25, 
        add.expr = abline(v=seplines, h=6.5, col="grey50"))
```


## Classification

```{r}
source("/data1/famface01/command/misc/face_representations/misc/cv_glmnet.R")

snums <- as.numeric(factor(ssubs))

lasso.coefs <- laply(1:ncol(std.rdats2), function(i) {
  tmp <- run_cvglmnet(X[,-1], std.rdats2[,i], foldid=snums, alpha=1, parallel=F)
  print(tmp$bestfit$val)
  cfs <- tmp$bestfit$coef[-1][-c(1:12)]
  names(cfs) <- colnames(X[,-1][,-c(1:12)])
  cfs
}, .parallel=T)
colnames(lasso.coefs) <- sub("smats", "", colnames(lasso.coefs))
rownames(lasso.coefs) <- rnames

round(lasso.coefs, 2)
```

```{r}
cols <- colorRampPalette(brewer.pal(9, "YlOrRd"))(100)
#all.grps2 <- c("face",all.grps)
all.grps2 <- all.grps
ccols <- factor(all.grps2, levels=levels(factor(all.grps2)), 
                labels=rev(brewer.pal(length(unique(all.grps2)), "Set3")))
ccols <- as.character(ccols)

mat <- abs(lasso.coefs)
#colnames(mat) <- sub("smats", "", colnames(mat))

tmat <- mat# * (abs(mat) > 1.96)
zlim <- range(abs(tmat[tmat!=0]))
tmat[tmat==0] <- NA

# separator lines
seplines <- c(0,cumsum(rle(all.grps2)$lengths)) + 0.5

heatmap(tmat, scale="none", col=cols, ColSideColors = ccols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25, 
        add.expr = abline(v=seplines, h=6.5, col="grey50"))
```

```{r}
library(covTest)
lasso.sig <- alply(std.rdats2, .(2), function(y) {
  a <- lars(X[,-1], y)
  tmp <- covTest(a, X[,-1], std.rdats2[,3])
  inds <- tmp$results[,1][tmp$results[,3] < 0.05]
  sub("mats", "", sub("s", "", colnames(X[,-1])))[inds]
}, .parallel=T)
names(lasso.sig) <- rnames
lasso.sig
```

```{r}
library(lassoscore)

lasso.sigs2 <- laply(1:ncol(std.rdats2), function(i) {
  tmp <- run_cvglmnet(X[,-1], std.rdats2[,i], foldid=snums, alpha=1, parallel=F)
  print(tmp$bestfit$val)
  tmp2 <- lassoscore(std.rdats2[,i], X[,-1], lambda=tmp$bestfit$lam)
  sigs <- tmp2$p.model[-c(1:12)]
  names(sigs) <- colnames(X[,-1][,-c(1:12)])
  sigs
}, .parallel=T)
colnames(lasso.sigs2) <- sub("smats", "", colnames(lasso.sigs2))
rownames(lasso.sigs2) <- rnames

lasso.sigz <- qt(lasso.sigs2, Inf, lower.tail=F)
```

```{r}
cols <- colorRampPalette(brewer.pal(9, "YlOrRd"))(100)
#all.grps2 <- c("face",all.grps)
all.grps2 <- all.grps
ccols <- factor(all.grps2, levels=levels(factor(all.grps2)), 
                labels=rev(brewer.pal(length(unique(all.grps2)), "Set3")))
ccols <- as.character(ccols)

mat <- lasso.sigz
#colnames(mat) <- sub("smats", "", colnames(mat))

tmat <- mat * (mat > 1.96)
zlim <- range(tmat[tmat!=0])
tmat[tmat==0] <- NA

# separator lines
seplines <- c(0,cumsum(rle(all.grps2)$lengths)) + 0.5

heatmap(tmat, scale="none", col=cols, ColSideColors = ccols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25, 
        add.expr = abline(v=seplines, h=6.5, col="grey50"))
```
