---
title: "GLM+Lasso Predicted FaceFeats"
author: "Zarrar Shehzad"
date: "March 5, 2017"
output: html_document
---

## Setup

Load a bunch of packages and functions.

```{r}
# Path for my own packages
if (!any(.libPaths() == "/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2")) .libPaths(c("/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2", .libPaths()))
if (!any(.libPaths() == "/home/zshehzad/R_libs")) .libPaths(c("~/R_libs", .libPaths()))

# General workhorse function
library(plyr)

# Parallelization
suppressMessages(library(doMC))
registerDoMC(24)

# If we were to use ggplot2 and other plotting needs
library(RColorBrewer)
library(ggplot2)
source("/data1/famface01/command/encoding/FirstPass/plot_functions.R")

# This gets us the simple_lm function for faster GLMs
source("/data1/famface01/command/encoding/SubRois_Unfam/lm_functions.R")

## For heatmap.2
#suppressMessages(library(gplots))
## For our own custom convolution
#source("/data1/famface01/command/encoding/ShapesAnalysis/000_funs_load_convolve.R")
```

And some general variable of interest.

```{r}
subjects <- sprintf("sub%02i", 1:6) # again skipping sub01
#indir    <- "/data1/famface01/analysis/encoding/ShapeAnalysis/data"
rnames   <- c("r.vATL","r.aFFA", "r.pFFA", "r.OFA", "r.EBA", 'r.Amyg', 
              "l.vATL", "l.FFA", "l.OFA", "l.EBA", 'l.Amyg')
```


### Load

#### Predicted/Residual Face Features

Load the convolved features for the raw data and then the convolved predicted/residual face features.

```{r}
ifile <- "/data1/famface01/analysis/misc/320_roi_task_activity/22_convolve_facefeats.rda"
load(ifile, verbose=T)

ifile <- "/data1/famface01/analysis/misc/320_roi_task_activity/24_predict_convolve.rda"
load(ifile, verbose=T)
```

#### ROI Data

Then first, get the ROI data.

```{r}
load.cur <- function(subj) {
  indir <- "/data1/famface01/analysis/encoding/ShapeAnalysis/data"
  infile <- sprintf("%s/roi_n_more_%s.rda", indir, subj)
  dat <- NULL
  load(infile)
  dat
}

dat.vols <- lapply(subjects, load.cur)
names(dat.vols) <- subjects
```

We compile the average of each ROI (for now). And load the standard space ROIs. We won't use the `rdats` actually.

```{r}
lst.rdats <- lapply(dat.vols, function(dat) {
  rdats <- sapply(dat$fmri$dat, rowMeans)
  rdats
})
rdats <- do.call(rbind, lst.rdats)

load("/data1/famface01/analysis/misc/320_roi_task_activity/std_roi_dat.rda", verbose=T)
```



## Regressions: All Data

```{r}
# Raw vals
X <- model.matrix(~ssubs + smcs + sfaces + smats)
fit1 <- simple_lm(std.rdats2, X)
fit1$tvals
```

Plot as heatmap

```{r}
cols <- colorRampPalette(rev(brewer.pal(11, "RdBu")))(100)
all.grps2 <- c("face",all.grps)
ccols <- factor(all.grps2, levels=levels(factor(all.grps2)), 
                labels=rev(brewer.pal(length(unique(all.grps2)), "Set3")))
ccols <- as.character(ccols)

mat <- t(fit1$tvals[-c(1:12),])
colnames(mat) <- sub("smats", "", colnames(mat))

tmat <- mat * (abs(mat) > 1.96)
#hc.cols <- hclust(dist(t(tmat)), method="ward.D2")
zlim <- max(abs(tmat)) * c(-1,1)
tmat[tmat==0] <- NA

# separator lines
seplines <- c(0,cumsum(rle(all.grps2)$lengths)) + 0.5

heatmap(tmat, scale="none", col=cols, ColSideColors = ccols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25, 
        add.expr = abline(v=seplines, h=6.5, col="grey50"))
```

```{r}
fit0 <- simple_lm(std.rdats.all$r.EBA, X)

mat <- t(fit0$tvals[-c(1:12),])
colnames(mat) <- sub("smats", "", colnames(mat))

tmat <- mat * (abs(mat) > 1.96)
hc.rows <- hclust(dist(tmat), method="ward.D2")
zlim <- max(abs(tmat)) * c(-1,1)
tmat[tmat==0] <- NA

# separator lines
seplines <- c(0,cumsum(rle(all.grps2)$lengths)) + 0.5

heatmap(tmat, scale="none", col=cols, ColSideColors = ccols, 
        zlim=zlim, Rowv=as.dendrogram(hc.rows), Colv=NA, labRow = F, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25, 
        add.expr = abline(v=seplines, h=6.5, col="grey50"))
```


```{r}
# Predicted vals
preds  <- spreds1[,c(1:8,30:31)]#,9:10,12,13:17,19:21,23)]
resids <- sresids1[,c(1:8,30:31)]#,9:10,12,13:17,19:21,23)]
X      <- model.matrix(~ssubs + smcs + sfaces + preds + resids)
fit2 <- simple_lm(std.rdats2, X[,1:17])
fit2$tvals
```

```{r}
cols <- colorRampPalette(rev(brewer.pal(11, "RdBu")))(100)
all.grps2 <- c("face",all.grps)
ccols <- factor(all.grps2, levels=levels(factor(all.grps2)), 
                labels=rev(brewer.pal(length(unique(all.grps2)), "Set3")))
ccols <- as.character(ccols)

mat <- t(fit2$tvals[-c(1:12),][c(2:23),])
colnames(mat) <- sub("preds", "", colnames(mat))

tmat <- mat * (abs(mat) > 1.96)
#hc.cols <- hclust(dist(t(tmat)), method="ward.D2")
zlim <- max(abs(tmat)) * c(-1,1)
tmat[tmat==0] <- NA

# separator lines
seplines <- c(0,cumsum(rle(all.grps2)$lengths)) + 0.5

heatmap(tmat, scale="none", col=cols, ColSideColors = ccols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25, 
        add.expr = abline(v=seplines, h=6.5, col="grey50"))

heatmap(tmat, scale="none", col=cols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25)
```


```{r}
cols <- colorRampPalette(rev(brewer.pal(11, "RdBu")))(100)
all.grps2 <- c("face",all.grps)
ccols <- factor(all.grps2, levels=levels(factor(all.grps2)), 
                labels=rev(brewer.pal(length(unique(all.grps2)), "Set3")))
ccols <- as.character(ccols)

mat <- t(fit2$tvals[-c(1:12),][c(24:45),])
colnames(mat) <- sub("resid", "", colnames(mat))

tmat <- mat * (abs(mat) > 1.96)
#hc.cols <- hclust(dist(t(tmat)), method="ward.D2")
zlim <- max(abs(tmat)) * c(-1,1)
tmat[tmat==0] <- NA

# separator lines
seplines <- c(0,cumsum(rle(all.grps2)$lengths)) + 0.5

heatmap(tmat, scale="none", col=cols, ColSideColors = ccols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25, 
        add.expr = abline(v=seplines, h=6.5, col="grey50"))

heatmap(tmat, scale="none", col=cols, 
        zlim=zlim, Rowv=NA, Colv=NA, 
        margins=c(9,5), cexCol = 1.25, cexRow = 1.25)
```


## Regressions: Only Traits

So now I want to be able to compare the significance of different regions to the stuff I ran before. So I just spit out a table for the regression of predicted and residuals using the 6 trait factor scores.

```{r}
tpred <- spreds1[,1:6]#; colnames(tpred) <- paste("pred", colnames(tpred), sep=".")
rpred <- sresids1[,1:6]#; colnames(rpred) <- paste("resid", colnames(rpred), sep=".")

fit <- lm(std.rdats2 ~ ssubs + smcs + sfaces + rpred + tpred)
sfit <- summary(fit)

tvals <- sapply(sfit, function(x) x$coefficients[-c(1:13),3])
rownames(tvals) <- substr(rownames(tvals), 0, 10)
rownames(tvals) <- sub("tpred", "pred.", rownames(tvals))
rownames(tvals) <- sub("rpred", "resid.", rownames(tvals))
colnames(tvals) <- rnames
round(t(tvals * (abs(tvals) > 1.96)), 2)

sfit$`Response r.vATL`$
       
X <- model.matrix(~ssubs + smcs + sfaces + tpred + rpred)
fit1 <- simple_lm(std.rdats2, X)
fit1$tvals

```

