---
title: "TS Convolution"
author: "Zarrar Shehzad"
date: "February 17, 2017"
output: html_document
---

Looking at doing convolution right for time-series data. I have some sample 
data being used here that will be used to predict the brain data. We also have
the HRF that we will be convolved with the data here.

```{r}
if (!any(.libPaths() == "/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2")) .libPaths(c("/home/zshehzad/R/x86_64-redhat-linux-gnu-library/3.2", .libPaths()))
if (!any(.libPaths() == "/home/zshehzad/R_libs")) .libPaths(c("~/R_libs", .libPaths()))

chrf <- NULL; feats <- NULL
load("z_convolve_vars.rda")
```

## Plain R

Here I make use of plain R data for the convolution. The default R options mean
that a circular convolution is done but we need to pad the data so the beginning
of our time-series isn't convolved with the end of the time-series. The result
of doing this though is that R returns the padded time-series and we need to just
unpad the results. You can see from the result in red, the beginning of the 
signal is now proper, everything else is the same.

```{r}
system.time(s.conv0 <- convolve(chrf, rev(feats)))
system.time(s.conv1 <- convolve(chrf, rev(feats), type = "open")[1:length(feats)])
plot.ts(cbind(s.conv0, s.conv1), plot.type = "single", col=1:2)
```

## FFTW

Now wee try out the fftw function in `fftwtools` to speed things up. Haha so
for some reason this is all running slower than I'd want.

```{r}
  library(fftwtools)
  library(fftw)

  n <- 2**16
  chrf <- rnorm(n)
  
  system.time(fft(fft(chrf) * Conj(fft(chrf)), inverse=TRUE))
  
  system.time(p <- fftw::planFFT(chrf))
  system.time(IFFT(FFT(chrf, plan=p) * Conj(FFT(chrf, plan=p)), plan=p, scale=F))
  
  system.time(for (i in 1:10) tmp1 <- fft(chrf))
  system.time(for (i in 1:10) tmp2 <- fftwtools::fftw(chrf))
  system.time(for (i in 1:10) tmp3 <- fftw::FFT(chrf))
  system.time(p <- fftw::planFFT(chrf))
  system.time(for (i in 1:10) tmp3 <- fftw::FFT(chrf, plan=p))
  
  system.time(for (i in 1:6) tmp1 <- fft(chrf))
  system.time(mtmp2 <- mvfftw(cbind(chrf,chrf,chrf,chrf,chrf,chrf,chrf)))
  
  
  
  head(tmp3)
  head(tmp1)
```


```{r}
library(fftw)

# linear convolution
  
x <- chrf; y <- feats
n <- length(x)
ny <- length(y)

# test shorter padding
tmp <- diff(chrf) < 1e-8
tmp2 <- rle(tmp)
npad <- length(chrf) - tmp2$lengths[length(tmp2$lengths)] + 1

# pad...onl
n1 <- ny - 1
#n1 <- min(npad, n1)
x <- c(rep.int(0,n1), x)
n <- length(y <- c(y, rep.int(0, n - 1)))

# convolve...compare the two approaches
## note: here that 
system.time(x0 <- fft(fft(x) * Conj(fft(y)), inverse=TRUE))
system.time(x0 <- Re(x0)/n)

system.time(p <- fftw::planFFT(x))
system.time(x1 <- IFFT(FFT(x, plan=p) * Conj(FFT(y, plan=p)), plan=p, scale=F))
system.time(x1 <- Re(x1)/n)

all.equal(x0,x1)
```


Below we see the code to run this baby with one set of features.

```{r}
xref <- x1

x <- chrf; y <- rev(feats)
n <- length(x)
ny <- length(y)
if (n != ny) stop("x and y must be the same lengths")

# pad
n1 <- ny - 1
x <- c(rep.int(0,n1), x)
n <- length(y <- c(y, rep.int(0,n1)))

# convolve
system.time(p <- fftw::planFFT(x))
system.time(x1 <- IFFT(FFT(x, plan=p) * Conj(FFT(y, plan=p)), plan=p, scale=F))
x1 <- Re(x1)/n
x2 <- x1[1:ny]

plot.ts(x1[1:(ny+100)])
plot.ts(x2)

tmp <- convolve(chrf, rev(feats), type="open")
plot.ts(tmp[1:(length(feats)+1000)])

all.equal(x1, tmp)
```


```{r}
convolve.fftw <- function(x, y) {
  library(fftw)
  n  <- length(x)
  ny <- length(y)
  if (n != ny) stop("x and y must be the same lengths")
  
  # pad
  n1 <- ny - 1
  x <- c(rep.int(0,n1), x)
  n <- length(y <- c(y, rep.int(0,n1)))
  
  # convolve
  p <- fftw::planFFT(x)
  x1 <- IFFT(FFT(x, plan=p) * Conj(FFT(y, plan=p)), plan=p, scale=F)
  x1 <- Re(x1)/n
  x1 <- x1[1:ny]
  
  return(x1)
}

convolve.mfftw <- function(x, ys) {
  library(fftw)
  n  <- length(x)
  ny <- nrow(ys)
  if (n != ny) stop("x and y must be the same lengths")
  
  # pad
  n1 <- ny - 1
  x <- c(rep.int(0,n1), x)
  n <- length(x)
  ys0 <- ys
  ys <- matrix(0, n, ncol(ys))
  ys[1:ny,] <- ys0
  rm(ys0)
  
  # convolve
  p <- fftw::planFFT(x)
  xx <- FFT(x, plan=p)
  x1s <- sapply(1:ncol(ys), function(i) {
    Re(IFFT(xx * Conj(FFT(ys[,i], plan=p)), plan=p, scale=F))
  })
  x1s <- x1s/n
  x1s <- x1s[1:ny,]
  
  return(x1s)
}

# So we save some time with this multi-convolve thingy
ys <- cbind(feats,feats,feats,feats,feats)
system.time(convolve.mfftw(chrf, ys))
system.time(sapply(1:ncol(ys), function(i) convolve.fftw(chrf, ys[,i])))
system.time(sapply(1:ncol(ys), function(i) convolve(chrf, ys[,i], type='open')))
# 3/0.1
```
