---
title: "Layers-Representations"
author: "Zarrar"
date: "April 14, 2017"
output: html_document
---

We want to visualize properties of the neural network for an early, middle, and late layer to show how it slowly learns face identity, ignores unimportant features, and has improved representation for related features.

## Load

Libraries that will be relevant.

```{r}
library(plyr)
library(ggplot2)
suppressMessages(library(doMC))
registerDoMC(20)
```

Note that we first selected some of the layers and then later subselected of those to get early/middle/late.

```{r}
select.layers <- c(3,4,5,8,11,12,13,14:19,21:22,25,26)
select.layers2 <- c(4, 16, 26)
sl.inds <- select.layers %in% select.layers2
```

We first must load in all the feature ridge regressions and the identity classification results.

```{r}
load_obj <- function(f) {
    env <- new.env()
    nm <- load(f, env)[1]
    env[[nm]]
}
load_classify_obj <- function(f) {
  obj <- load_obj(f)
  if (length(obj) == length(select.layers)) {
    obj <- obj[sl.inds]
  }
  return(obj)
}

outdir <- "/data1/famface01/analysis/misc/400_nnet_specificity"

accs <- load_obj("accs.rda")
accs <- accs[select.layers2,]
### get within/between...a bit round-about
#accs2 <- load_obj("accs2.rda")
#accs2 <- accs2[,-c(1,1730,1631)]
#rowMeans(accs2[,grep("^win", colnames(accs2))])
#rowMeans(accs2[,grep("^btw", colnames(accs2))])

fpaths <- list.files(outdir, pattern="rda", full.names=T)
lst.classifys <- llply(fpaths, load_classify_obj, .progress="text")
names(lst.classifys) <- sub(".rda", "", sub("classify_layers_", "", basename(fpaths)))
## select the ones you want here
lst.classifys <- lst.classifys[c("pose", "luminance", "attractive", "age")]
```

## Visualize

### Format

Let's format the inputs as a data-frame for later displaying.

```{r}
# First combine into a matrix
cmat <- sapply(lst.classifys, function(x) sapply(x, function(xx) xx$mean.max.res))
mat <- cbind(accs[,1:2], cmat)
mat[,1] <- mat[,1]*100
dimnames(mat) <- list(
  Layers = c("Early", "Middle", "Later"), 
  Measures = c("Nearest-Neighbor Accuracy", "Within vs Between Videos", "Pose", "Luminance", "Attractive", "Age")
)
print(mat)

# Then convert to a dataframe
df.mat <- reshape2::melt(mat)
df.mat$Type <- factor(df.mat$Measures, levels=levels(df.mat$Measures), labels=rep(c("Cluster", "Negative", "Positive"), c(2,2,2)))
df.mat <- df.mat[,c(1,4,2,3)]
head(df.mat)
```

### Plot

Some setup.

```{r}
library(ggthemr)
library(RColorBrewer)

ggthemr('pale', type='outer', text_size=14, layout='plain')

outdir <- "/data1/famface01/figures/400_nnet_specificity"
if (!file.exists(outdir)) dir.create(outdir)
```

I'll do the clustering ones separately and here first.

```{r}
# Gets the Cluster Measures
sdf <- subset(df.mat, Type=="Cluster")
## nn accuracy
p1 <- ggplot(subset(sdf, Measures=="Nearest-Neighbor Accuracy"), aes(x=Layers, y=value, fill=Layers)) + 
  geom_bar(stat="identity") + 
  scale_fill_manual(values=rev(brewer.pal(7, "Spectral")[1:3])) + 
  facet_wrap(~Measures, scales = "free_y") + 
  ylab("Percent Accuracy") + 
  scale_y_continuous(breaks=95:100, expand=c(0,0)) + 
  expand_limits(y=100.5) + 
  coord_cartesian(ylim=c(95,100.5)) + 
  theme(axis.line.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        axis.line.x = element_line(color="black", size=1), 
        legend.position = "none")
## W/B Ratio
p2 <- ggplot(subset(sdf, Measures=="Within vs Between Videos"), aes(x=Layers, y=value, fill=Layers)) + 
  geom_bar(stat="identity") + 
  scale_fill_manual(values=rev(brewer.pal(7, "Spectral")[1:3])) + 
  facet_wrap(~Measures, scales = "free_y") + 
  ylab("Ratio W/B Distances ") + 
  scale_y_continuous(breaks=seq(0,0.5,by=0.1), expand=c(0,0)) + 
  expand_limits(y=0.6) + 
  #coord_cartesian(ylim=c(95,100.5)) + 
  theme(axis.line.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        axis.line.x = element_line(color="black", size=1), 
        legend.position = "none")

# Combine
# http://stackoverflow.com/questions/30280499/different-y-limits-on-ggplot-facet-grid-bar-graph
## save
p <- gridExtra::arrangeGrob(p1, p2, ncol=2)
ggsave(file.path(outdir, "nnet_clusters.png"), p, width=8, height=4)
ggsave(file.path(outdir, "nnet_clusters.pdf"), p, width=8, height=4)
## view
gridExtra::grid.arrange(p1, p2, ncol=2)
```

Now, I can do the negative variables. Really big drop in the later layer.

```{r}
# Gets the Cluster Measures
sdf <- subset(df.mat, Type=="Negative")
## Luminance
p1 <- ggplot(subset(sdf, Measures=="Luminance"), aes(x=Layers, y=value, fill=Layers)) + 
  geom_bar(stat="identity") + 
  scale_fill_manual(values=rev(brewer.pal(7, "Spectral")[1:3])) + 
  facet_wrap(~Measures, scales = "free_y") + 
  ylab(expression(r^2)) + 
  scale_y_continuous(breaks=seq(0,1,by=0.2), expand=c(0,0)) + 
  expand_limits(y=1.1) + 
  coord_cartesian(ylim=c(0,1.1)) + 
  theme(axis.line.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        axis.line.x = element_line(color="black", size=1), 
        legend.position = "none")
## Pose
p2 <- ggplot(subset(sdf, Measures=="Pose"), aes(x=Layers, y=value, fill=Layers)) + 
  geom_bar(stat="identity") + 
  scale_fill_manual(values=rev(brewer.pal(7, "Spectral")[1:3])) + 
  facet_wrap(~Measures, scales = "free_y") + 
  ylab(expression(r^2)) + 
  scale_y_continuous(breaks=seq(0,1,by=0.2), expand=c(0,0)) + 
  expand_limits(y=1.1) + 
  coord_cartesian(ylim=c(0,1.1)) + 
  theme(axis.line.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        axis.line.x = element_line(color="black", size=1), 
        legend.position = "none")

# Combine
# http://stackoverflow.com/questions/30280499/different-y-limits-on-ggplot-facet-grid-bar-graph
## save
p <- gridExtra::arrangeGrob(p1, p2, ncol=2)
ggsave(file.path(outdir, "nnet_neg_lum+pose.png"), p, width=8, height=4)
ggsave(file.path(outdir, "nnet_neg_lum+pose.pdf"), p, width=8, height=4)
## view
gridExtra::grid.arrange(p1, p2, ncol=2)
```

And now the positive.

```{r}
# Gets the Cluster Measures
sdf <- subset(df.mat, Type=="Positive")
## Luminance
p1 <- ggplot(subset(sdf, Measures=="Age"), aes(x=Layers, y=value, fill=Layers)) + 
  geom_bar(stat="identity") + 
  scale_fill_manual(values=rev(brewer.pal(7, "Spectral")[1:3])) + 
  facet_wrap(~Measures, scales = "free_y") + 
  ylab(expression(r^2)) + 
  scale_y_continuous(breaks=seq(0,1,by=0.2), expand=c(0,0)) + 
  expand_limits(y=1.1) + 
  coord_cartesian(ylim=c(0,1.1)) + 
  theme(axis.line.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        axis.line.x = element_line(color="black", size=1), 
        legend.position = "none")
## Pose
p2 <- ggplot(subset(sdf, Measures=="Attractive"), aes(x=Layers, y=value, fill=Layers)) + 
  geom_bar(stat="identity") + 
  scale_fill_manual(values=rev(brewer.pal(7, "Spectral")[1:3])) + 
  facet_wrap(~Measures, scales = "free_y") + 
  ylab(expression(r^2)) + 
  scale_y_continuous(breaks=seq(0,1,by=0.2), expand=c(0,0)) + 
  expand_limits(y=1.1) + 
  coord_cartesian(ylim=c(0,1.1)) + 
  theme(axis.line.y = element_blank(), 
        panel.grid.major.x = element_blank(), 
        axis.line.x = element_line(color="black", size=1), 
        legend.position = "none")

# Combine
# http://stackoverflow.com/questions/30280499/different-y-limits-on-ggplot-facet-grid-bar-graph
## save
p <- gridExtra::arrangeGrob(p1, p2, ncol=2)
ggsave(file.path(outdir, "nnet_pos_age+attractive.png"), p, width=8, height=4)
ggsave(file.path(outdir, "nnet_pos_age+attractive.pdf"), p, width=8, height=4)
## view
gridExtra::grid.arrange(p1, p2, ncol=2)
```


```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
